NGO analysis

### 2022-07-31 Dashboard/NGO Analysis dashboard alpha v003.Rmd
Updating maximum scale function to use excel_test.

  ## scale maximum--------------------------------------------------------------
  # Reactive function to create the maximum value for revenue and expenses plots
  maximum <- reactive({
    if (datatest() == TRUE) {
      NA
    } else {
      # reading the Excel sheet anew
      read_excel(input$excel$datapath) |>
        # removing the firm and sub-category columns
        select(-Firm, -`Sub-category`) |>
        # filtering to retain only revenue and expenses entries
        filter(Category == "Revenue" | Category == "Expenses") |>
        # grouping and summarising to calculate maximum value
        group_by(Year, Category) |>
        summarise(
          sum = sum(Value, na.rm = TRUE)
        ) |>
        # Creating list of sums
        pull() |>
        # selecting the highest value
        max()
    }
  })

@@

## Functions to read Excel file ------------------------------------------------
### First Excel transformation - creating df used by NGO title function---------
widen_excel_test <- function(file) {
  # Reading Excel file
  read_excel(file) |>
    # cleaning names to enable later operations
    clean_names()
}

>>>>

  ## scale maximum--------------------------------------------------------------
  # Reactive function to create the maximum value for revenue and expenses plots
  # the tests are probably not necessary, but included to be on the safe side
  maximum <- reactive({
    if (datatest() == TRUE || setequal(
      names(exceldata()),
      c("year", "firm", "category", "sub_category", "name", "value")
    )) {
      NA
    } else {
      excel_test() |>
        # removing the firm and sub-category columns
        select(-firm, -sub_category) |>
        # filtering to retain only revenue and expenses entries
        filter(category == "Revenue" | category == "Expenses") |>
        # grouping and summarising to calculate maximum value
        group_by(year, category) |>
        summarise(
          sum = sum(value, na.rm = TRUE)
        ) |>
        # Creating list of sums
        pull() |>
        # selecting the highest value
        max()
    }
  })

@@

## Functions to read Excel file ------------------------------------------------
### First Excel transformation -------------------------------------------------
# creating df used by NGO title function maximum scale function
widen_excel_test <- function(file) {
  # Reading Excel file
  read_excel(file) |>
    # cleaning names to enable later operations
    clean_names()
}
